# Find AAA Games

## Find AAA Developers

First, we try to find AAA developers. We draw the Cleveland dot plots of their sales volume and sales. We draw vertical lines of top 1% and top 0.5% for sales volume and sales. We don’t show smaller companies on the plot.

```{r fig.height=9, fig.width=8, echo = FALSE}
developer_data <- company_data %>% group_by(developer) %>% dplyr::summarise(sales = sum(sales),money = sum(money))
company_data %>% group_by(developer) %>% dplyr::summarise(sales = sum(sales)) %>% 
  filter(sales > 10000000) %>% 
  ggplot() + geom_point(aes(x = reorder(developer, -sales), y = sales)) + 
  geom_hline(yintercept = quantile(developer_data$sales, 0.99, na.rm = TRUE), color = "Pink") +
  annotate("text", x = 25.5, y = 11000000, label = "Top 1%", color = "darkred") +
  geom_hline(yintercept = quantile(developer_data$sales, 0.995, na.rm = TRUE), color = "Pink") +
  annotate("text", x = 25.5, y = 25000000, label = "Top 0.5%", color = "darkred") +
  scale_y_continuous(trans = log10_trans(),
    breaks = trans_breaks("log10", function(x) 10^x),
    labels = trans_format("log10", math_format(10^.x))) + 
  xlab("Developers") + ylab("Sales Volume") + 
  labs(title = "Total Sales Volume of large companies", subtitle = "Focus on developers of sales volume over 10,000,000") + 
  coord_flip() + blue_theme()
```

```{r fig.height=9, fig.width=8, echo=FALSE}
company_data %>% group_by(developer) %>% 
  dplyr::summarise(money = sum(money)) %>% 
  filter(money > 100000000)  %>%
  ggplot() + geom_point(aes(x = reorder(developer, -money), y = money)) + 
  geom_hline(yintercept = quantile(developer_data$money, 0.99, na.rm = TRUE), color = "Pink") +
  annotate("text", x = 25.5, y = 130000000, label = "Top 1%", color = "darkred") +
  geom_hline(yintercept = quantile(developer_data$money, 0.995, na.rm = TRUE), color = "Pink") +
  annotate("text", x = 25.5, y = 240000000, label = "Top 0.5%", color = "darkred") +
  scale_y_continuous(trans = log10_trans(),
    breaks = trans_breaks("log10", function(x) 10^x),
    labels = trans_format("log10", math_format(10^.x))) + 
  xlab("Developers") + ylab("Sales Value(dollar)") + 
  labs(title = "Total Sales of large companies", subtitle = "Focus on developers of sales over 100,000,000") + 
  coord_flip() +
  blue_theme()
```

```{r, echo=FALSE}
aaa_developer <- company_data %>% group_by(developer) %>% 
  dplyr::summarise(n = n(), sales = sum(sales), money = sum(money)) %>%
  filter((sales > quantile(sales, 0.995, na.rm = TRUE)) | (money > quantile(money, 0.995, na.rm = TRUE)))

aaa <- company_data %>% filter(developer %in% aaa_developer$developer)
```

We pick the top 0.5% companies in both graph as our AAA companies. There are 18 companies in total which is an appropriate number considering we want the major companies. 

## Overview of AAA Devolpers

### Number of Games

```{r, echo = FALSE}
aaa_developer %>% ggplot() + geom_point(aes(x = reorder(developer,-money), y = n)) + coord_flip() +
  xlab("Developers") + ylab("Number of Games") + 
  labs(title = "Number of Games of AAA Developers", subtitle = "Sort by the total sales value of developers") + 
  blue_theme()
```

We reorder the developers by sales and show how many games they released. We are surprised that Pubg Corporation tops the sales but only has one game released. 

### Sales Volume

```{r fig.height=7, fig.width=8, echo=FALSE, warning = FALSE}
aaa_developer %>% 
  ggplot(aes(x = reorder(developer,-sales), y = sales,
                 label = paste(as.character(round(sales/1000000)),"million"))) + 
  geom_point() + 
  scale_y_continuous(limits = c(6500000,600000000), trans = log10_trans(),
    breaks = trans_breaks("log10", function(x) 10^x),
    labels = trans_format("log10", math_format(10^.x))) + 
  geom_text(vjust=-0.6, colour = "darkblue", size = 3.5) + coord_flip() +
  xlab("Developers") + ylab("Sales Volume") + 
  labs(title = "Sales Volume of AAA Companies") + 
  blue_theme()
```

In the sales plot of AAA companies, Valve surpasses Pubg. We claim that it’s because Valve has more low-price games or free games. We can examine it later by showing their free games.

### Total Sales

```{r fig.height=7, fig.width=8, echo=FALSE, warning = FALSE}
aaa_developer %>% ggplot(aes(x = reorder(developer,-money), y = money, label = ifelse(money == 1,0, paste(as.character(round(money/1000000, digits = 2)),"million")))) + 
  geom_point() + 
  scale_y_continuous(limits = c(200000000,2800000000), trans = log10_trans(),
    breaks = trans_breaks("log10", function(x) 10^x),
    labels = trans_format("log10", math_format(10^.x))) + 
  geom_text(vjust=-0.6, colour = "darkblue", size = 3.5) +
  coord_flip() +
  xlab("Developers") + ylab("Sales(dollar)") + 
  labs(title = "Sales of AAA Companies") + 
  blue_theme()
```

We can see that the Pubg exceeds Valve in sales value. Pubg Corporation with just one game got much more money than all the other companies. Pubg is so popular!

## Games of AAA Companies

```{r, echo=FALSE}
knitr::include_app("https://jerrysjhe.shinyapps.io/final_5/", height = "630px")
```

In this shiny app, users can select and view the data themselves. Choosing the AAA developer and variable, it draws a dot plot of the certain variable of certain developer. The available variables are: "Average playtime", "Median playtime", "Ratio", "Sales Volume", "Price" and "Sales". We can have an overview of the games of AAA developers and their performance.

If you are a Steam player, you can see many familiar names on it, such as Fallout, The Elder Scrolls, Portals. Feel free to find the games you like and see their performance.
